Flexible Binary Instrumentation for the Kernel

### 2013-11-11 VEE-14/paper.tex
Last night's work before leaving for home

\begin{figure}[t!]
\lstset{language=C, tabsize=2, stepnumber=1}
\begin{lstlisting}[basicstyle=\footnotesize\ttfamily]
FUNCTION_WRAPPER(MODULE, __kmalloc, (size, gfp), {
  void *addr = __kmalloc(size, gfp);
  if(is_valid_address(addr)) {
    add_watchpoint(addr, addr, size);
  }
  return addr;
})
\end{lstlisting}
\caption{Example module function wrapper for the \texttt{\_\_kmalloc} memory allocator. This allocator adds an ``address watchpoint", which Granary's module memory leak detector uses to track the liveness of module-allocated memory. Every access of a ``watched address" marks the associated memory as live within the current epoch. Memory that has not been live for several consecutive epochs is treated as a potential leak, and a is checked for reachability using a heap memory scanner.}
\label{fig:malloc_wrapper}
\end{figure}

Granary's module memory leak detector is an example application that uses the selectivity of wrappers (with respect to their calling context) to distinguish between module-allocated and kernel-allocated memory (\Cref{fig:malloc_wrapper}).

%Granary can instrument, or not instrument, particular function

@@

On-demand instrumentation makes use

>>>>

@@

Demand-based instrumenetation blah blah blah
